---
title: "PACT Experiment 1A"
author: "Shawn Cummings and Rachel Theodore"
date: /today
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo=FALSE, include=FALSE}
library(tidyverse)
library(Rmisc)
library(dplyr)
library(stringr) 
library(magrittr) #2-sided pipes (%<>%)
```

## Data import and counter-balance check

First, we import all spreadsheets for all conditions intended to be run.
For each spreadsheet, we additionally check against our counterbalancing variables for that experiment and condition. 

```{r}
setwd("../Spreadsheets/")
spreadsheet.List <- list.files(pattern = "*.csv")
for (i in 1:length(spreadsheet.List))
  assign(spreadsheet.List[i],
         read.csv(spreadsheet.List[i], na.strings = c("", " ", "NA")))

d <- rbind(`PACT-1a-001.csv`,
           `PACT-1a-002.csv`,
           `PACT-1a-003.csv`,
           `PACT-1a-004.csv`,
           `PACT-1a-005.csv`,
           `PACT-1a-006.csv`,
           `PACT-1a-007.csv`,
           `PACT-1a-008.csv`)

unique(d$dose) #check that Dose, Test, Bias.Joanne, and Button1 are all correct

#d.002 <- read.csv(")


# conditions <- c("001", "002", "003", "004", "005", "006", "007", "008")
# dose <- c("1x")
# test.Type <- c("Blocked")
# test.Button1 <- c("# ASI", "# ASI", "# ASI", "# ASI", "# ASHI", "# ASHI", "# ASHI", "# ASHI")
# bias.Joanne <- c("SH", "SH", "SS", "SS", "SH", "SH", "SS", "SS")
# first.Test.Block <- c("Peter", "Joanne", "Peter", "Joanne", "Peter", "Joanne", "Peter", "Joanne")
# 
# d.counterbalances <- data.frame(conditions, dose, test.Type, test.Button1, bias.Joanne, first.Test.Block)




#d <- rbind(d.001, d.002, etc.)
d <- d.001


exposure.Trials <- d %>%
  filter(phase == "Exposure") %>%
  nrow()

test.Trials <- d %>%
  filter(phase == "Test") %>% #works differently for blocked versus mixed test
  nrow()

exposure.Trials

```
## Additional columns of interest

Using a parse of audio file used, we generate a number of columns informative towards condition. These *should* be redundant with hard-coded columns from the spreadsheet, but are included as a check against anything being awry.
```{r}
d %<>%
  separate(
    audio, c("audio.Construction", "audio.WordType", "audio.number", "audio.word"), sep = "_", remove=FALSE) %>%
  mutate(
    bias =
      case_when(
        fricative == "SS" & type == "Clear" ~ "SH",
        fricative == "SH" & type == "Ambiguous" ~ "SH",
        fricative == "SS" & type == "Ambiguous" ~ "SS",
        fricative == "SH" & type == "Clear" ~ "SS",
        T ~ NA_character_),
    type.Coded =
      case_when(
        substr(audio.WordType, 1, 1) == "X" ~ "Ambiguous",
        substr(audio.WordType, 1, 1) == "s" ~ "Clear",
        audio.WordType == "Test" ~ "Test",
        audio.WordType == "FW" ~ "Filler",
        T ~ NA_character_),
    fricative.Coded = 
      case_when(
        audio.WordType %in% c("Xsh", "sh") ~ "SH",
        audio.WordType %in% c("Xs", "s") ~ "SS",
        T ~ NA_character_),
    talker.Coded = 
      case_when(
        substr(audio.Construction, 1, 2) == "f1" ~ "Joanne",
        substr(audio.Construction, 1, 2) == "pe" ~ "Peter",
        T ~ NA_character_))
```
### Check for mismatches

Return any rows where the autocoded versus manually entered values for type, talker, or fricative don't match. This *should* return 0 rows.
```{r}
d %>%
  mutate(coding.Mismatch =
           case_when(
             is.na(audio) ~ F,
             type == type.Coded &
               talker == talker.Coded &
               (fricative == fricative.Coded |
                  (is.na(fricative) &
                      is.na(fricative.Coded))) ~ F,
             T ~ T)) %>%
  filter(coding.Mismatch == T) %>%
  select(condition, audio,
         type, type.Coded,
         talker, talker.Coded,
         fricative,fricative.Coded,
         coding.Mismatch) 
```


